Singapore's Public Housing Affordability

### 2023-11-14 datastory.qmd
Project Update

library(ggplot2)

data <- data.frame(
  category = c("A", "B", "C", "D"),
  value = c(23, 45, 12, 78)
)

ggplot(data, aes(x = category, y = value)) +
  geom_bar(stat = "identity") +
  theme_minimal() +
  labs(title = "Simple Bar Graph", x = "Category", y = "Value")

```
<p style="text-align: justify;">
The interactive graph above compares 
</p>

>>>>

<iframe height="550" width="100%" frameborder="no" src="https://mrzknrns.shinyapps.io/bargraph/">

<p style="text-align: justify;">
The interactive graph above compares 
</p>
